---
title: "Data dictionary, Exploratory Data Analysis - UMAA"
author: "Sandeep Gangarapu"
output: html_document
---
  
  
```{r echo=FALSE, warning=FALSE}
suppressPackageStartupMessages(
  {
    library(ggplot2)
    library(dplyr)
    library(tidyr)
    library(DataExplorer)
    library(dlookr)
    library(data.table)
  })

# https://cran.r-project.org/web/packages/dlookr/vignettes/EDA.html
# https://towardsdatascience.com/simple-fast-exploratory-data-analysis-in-r-with-dataexplorer-package-e055348d9619
```


We first look at all the files in the database

```{r echo=FALSE, warning=FALSE}
setwd("G:\\My Drive\\Research\\UMAA\\Data\\files\\Initial Data Files Cleaned")

#membership <- read.csv("membership_cleaned.csv")
#individual <- read.csv("individual_info_cleaned.csv")
#academic <- read.csv("academic_cleaned.csv")
emails <- fread("emails_cleaned.csv")
#events <- read.csv("events_cleaned.csv")
#engagement <- read.csv("engagement_cleaned.csv")

```

individual_info_cleaned.csv - This file contain individual data and the attributes.

"ID_DEMO" - Unique individual identifier
"ID_SPOUSE"
"MARITAL_STATUS"          
"GENDER"
"BIRTH_YEAR"
"AGE"
"ZIP_CODE"
"IN_TC_METRO_AREA"
"HOUSEHOLD_INCOME" 
"MOST_RECENT_COLLEGE" - Which college they graduated from (CLA, MED, CSE)
"MOST_RECENT_GRAD_YEAR"
"ATHLETIC_INTEREST"
"TRAVEL_INTEREST"
"MEMBERSHIP_TYPE_CODE" - A(annual), L(lifetime), X??
"MEMBERSHIP_STATUS_CODE" - C, P??  
"FIRST_EVER_START_DATE"
"EXP_DATE_LAST_MEMBERSHIP"

Primary Key = (ID_DEMO)


membership_cleaned.csv - This file has details on all the purchases of membership ever. Who purchase it, amount paid, when, form of payment, what type of memership etc.


"ID_DEMO" - Unique ID of the person       
"APPEAL_CODE" - ??
"FORM_OF_PAYMENT" - Cash or Creditcard 
"AMOUNT_PAID" - Money paid in $
"TRANSACTION_DATE" - Date of amount paid
"MEMBERSHIP_LEVEL" - Type of membership (Annual, lifetime etc)   
"ID_OF_RECORD_WITH_RELATIONSHIP" - Related accounts?
"MEMBERSHIP_RELATIONSHIP_TYPE." - ??
"FISCAL_YEAR" - Year of transaction date
s
Primary Key = (ID_DEMO, TRANSACTION_DATE)


academic_cleaned.csv - This file contains persons graduation year and the level of education
"ID_DEMO" - Unique individual identifier
"YEAR_GRAD" - Year when they graduated
"CODE_UM_DEGREE_LEVEL" - Bachelors, Masters etc. 14 levels

Primary Key = (ID_DEMO)


emails_cleaned.csv - This table has the details of every email even sent, sent to who, what is the email about etc
"CODE_PATH" - ?? Campaign? (1830 levels)
"ID_DEMO" - Unique individual identifier
"DATE_CONTACT" - Date email sent
"CODE_OUTCOME" - ?? (5 levels)
"YEAR_FISCAL" - Fiscal year of the email sent
"Status_Clicked" - email clicked or not
"broad_cat" - Category the email is related to (Sports, social, updates etc) (7 levels)

Primary Key = (ID_DEMO, CODE_PATH)


events_cleaned.csv - This table has info on the events conducted and the people who attended and what the event is about
"ID_DEMO" - Unique individual identifier
"NBR_GROUP" - ID of event??
"NAME_GROUP" - Name of the event
"DATE_EVENT" - Date of the event
"TYPE" - Group meeting or Event
"YEAR_FISCAL" - Year of event
"broad_cat" - Category of event

Primary Key = (ID_DEMO, NBR_GROUP)

engagement_cleaned.csv - ?? (The columns are unclear)

"ID_DEMO" - Unique individual identifier
"YEAR_FISCAL" - Year of engagement
"EVENT_ATTEND_ANNUAL"
"UMAA_MEMBER_ANNUAL"
"DONOR_ANNUAL"           
"VOLUNTEER_ANNUAL"
"STAY_INFORMED_ANNUAL"
"LOYALTY_ANNUAL"
"ENGAGEMENT_TOTAL_ANNUAL"
"ENGAGEMENT_LEVEL_ANNUAL"
"EVENT_ATTEND_LIFE"
"UMAA_MEMBER_LIFE"
"DONOR_LIFE"
"VOLUNTEER_LIFE"
"STAY_INFORMED_LIFE"     
"LOYALTY_LIFE"
"ENGAGEMENT_TOTAL_LIFE"
"ENGAGEMENT_LEVEL_LIFE"  



Issues:
1. MEMBERSHIP_TYPE_CODE in Individual and MEMBERSHIP_LEVEL in membership are coded differently.
2. Why not merge individual and academic?


```{r}
# plot_missing(individual)
# plot_histogram(individual)
# plot_density(individual)
# plot_correlation(individual, type = 'continuous')
# plot_bar(individual)
#create_report(membership, output_file='membership_eda.html')
#create_report(academic, output_file='academic_eda.html')
#create_report(events, output_file='events_eda.html')
#create_report(emails, output_file='emails_eda.html')

# eda_report(individual)

```
