---
title: "Membership Analysis - UMAA"
author: "Sandeep Gangarapu"
output: html_document
---
  
  
```{r echo=FALSE, warning=FALSE}
suppressPackageStartupMessages(
  {
    library(ggplot2)
    library(dplyr)
    library(tidyr)
    library(DataExplorer)
    library(dlookr)
  })

# https://cran.r-project.org/web/packages/dlookr/vignettes/EDA.html
# https://towardsdatascience.com/simple-fast-exploratory-data-analysis-in-r-with-dataexplorer-package-e055348d9619
```


We first look at all the files in the database

```{r echo=FALSE, warning=FALSE}
setwd("G:\\My Drive\\Research\\UMAA\\Data\\files\\Initial Data Files Cleaned")

membership <- read.csv("membership_cleaned.csv")
individual <- read.csv("individual_info_cleaned.csv")

```



Active membership

- Lifetime members
- Annual membership not expired
```{r}
length(unique(membership$ID_DEMO))
length(unique(individual$ID_DEMO))
table(individual$MEMBERSHIP_STATUS_CODE, individual$MEMBERSHIP_TYPE_CODE)
```

only 27523 of 484712 (5.6%) are current members.

Half of the current members seem to be lifetime members.

4660 out of 10470 (almost 50%) of current annual members paid 0$ for membership.

Most freq categoris:
UMAA Annual Membership (Single Complimentary) 
                                                         746 
             UMAA Annual Membership (Joint 3 Year Secondary) 
                                                         860 
                    UMAA Annual Membership (Joint Secondary) 
                                                        1657 
               UMAA Annual Membership (Single New Grad Comp) 
                                                        3392
                                                        
```{r}
a <- individual %>% filter(MEMBERSHIP_STATUS_CODE=='C' & MEMBERSHIP_TYPE_CODE=='A') %>% select(ID_DEMO, FIRST_EVER_START_DATE, EXP_DATE_LAST_MEMBERSHIP, IN_TC_METRO_AREA)
e <- individual %>% filter(MEMBERSHIP_STATUS_CODE=='C' & MEMBERSHIP_TYPE_CODE=='A' & IN_TC_METRO_AREA == 'Y' ) %>% select(ID_DEMO, FIRST_EVER_START_DATE, EXP_DATE_LAST_MEMBERSHIP, IN_TC_METRO_AREA)
b <- membership %>% select(ID_DEMO, MEMBERSHIP_LEVEL, FISCAL_YEAR, AMOUNT_PAID)

c <- merge(a, b, all.x = TRUE)

sort(table(droplevels(c$MEMBERSHIP_LEVEL)))
#prop.table(c$MEMBERSHIP_LEVEL)

d <- c %>% filter(AMOUNT_PAID!=0 & IN_TC_METRO_AREA=='Y') 
d <- c %>% filter(AMOUNT_PAID!=0) 

length(unique(d$ID_DEMO))
sort(table(droplevels(d$MEMBERSHIP_LEVEL)))

table(d$IN_TC_METRO_AREA)
```

Most annual members seem to be those who paid, not those where membership is given away.

